---
title: "Analysis of the Works of Jane Austen, Using the Bing, NRC, and the AFINN Sentiment Libraries"
by: Nipunjeet Gujral
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janeaustenr)
library(tidytext)
```

### grouping all the works of jane austen by books (6)
  > 
   * Sense & Sensibility 
   * Pride & Prejudice   
   * Mansfield Park      
   * Emma                
   * Northanger Abbey    
   * Persuasion

#####segmenting each book by chapters

#####unnesting the token words

```{r message=FALSE, warning=FALSE}
tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```


### Subsetting her works to just Pride and Prejudice
```{r message=FALSE, warning=FALSE}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")
```

### Appling the sentiment libraries to Pride and Prejudice


Applying the afinn library to Pride and Prejudice
```{r message=FALSE, warning=FALSE}
afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(score)) %>% 
  mutate(method = "AFINN")
```

Apply both the Bing and NRC sentiment libraries to Pride and Predujice
```{r message=FALSE, warning=FALSE}
bing_and_nrc <- bind_rows(pride_prejudice %>% 
                            inner_join(get_sentiments("bing")) %>%
                            mutate(method = "Bing"),
                          pride_prejudice %>% 
                            inner_join(get_sentiments("nrc") %>% 
                                         filter(sentiment %in% c("positive", 
                                                                 "negative"))) %>%
                            mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```

### Plotting the different sentiment libraries 

Combining the affin and bing_and_nrc dataframe
```{r message=FALSE, warning=FALSE}
bind_rows(afinn, bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```


