---
title: 'Analysis of Pride and Predjudice by Jane Austen, Using the Bing Sentiment Library'
by: Nipunjeet Gujral
---


```{r echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(janeaustenr)
library(tidytext)
```


### grouping all the works of jane austen by books (6)
  > 
   * Sense & Sensibility 
   * Pride & Prejudice   
   * Mansfield Park      
   * Emma                
   * Northanger Abbey    
   * Persuasion

#####segmenting each book by chapters

#####unnesting the token words
```{r message=FALSE, warning=FALSE}
tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```


### apply thing the 'bing' sentiment libary to her all 6 books

split each book by sentence

count the posative and sentiment word per sentence

sentiment = frequency of posative setement - frequency of negative setement  
```{r message=FALSE, warning=FALSE}
total_bing_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```


### graphing the sentiment of the sentences of text 
```{r}
ggplot(total_bing_sentiment, aes(index, sentiment, fill = book), xlab = "line numbers") +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```

